Compact Core Galaxies in the RESOLVE Survey

### 2016-05-10 paperdraft.tex
revisions

\title{Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Mark A. Norris\altaffilmark{3}}
\author{Callie Hood\altaffilmark{1}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{Ian Dell'Antonio\altaffilmark{4}}
\author{Samantha Dallas\altaffilmark{4}}
\author{Amanda J. Moffett\altaffilmark{1,5}}
\author{David V. Stark\altaffilmark{1}}
\author{the RESOLVE Team}
\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599, USA; emsnyder@live.unc.edu}
\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
\affil{$^4$Department of Physics, Brown Univsersity, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
way, Crawley, WA 6009, Australia}
\begin{abstract}
We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments. To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (XX\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements. The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk. We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs, dEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component. The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated. With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars. We find that CCGs naturally occur in a range of environments from isolated to cluster. We also derive velocity dispersions for 8 CCGs from Gemini IFU data and SOAR spectroscopy. Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively. Initial results show 7 CCGs clearly following the dissipative formation track.
\end{abstract}

@@

\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range between globular clusters (GCs) and normal elliptical galaxies (Es). Different types of CSSs include compact elliptical galaxies \citep[cEs;][]{Faber1973} and ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001}. There are many unanswered questions about how CSSs form and evolve through time. One fact that makes the study of these compact galaxies so intriguing is their apparent scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size. Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.

CSSs have radii ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.

In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated counterparts (dE,Ns) are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. dEs are typically larger than CSSs with radii ranging up to $\sim800$~pc, whereas dE,Ns may have larger envelopes with a core radius <$800$~pc \citep[e.g.,][]{Norris2014}. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and often quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016}. There is also some evidence that dE,Ns are the progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with radii up to 800~pc. The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}, but have also been found near groups \citep{Crnojevi2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$~Mpc.

Environment bears on formation scenarios in different ways. One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CCSs may rather be dissipatively formed like Es. However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process. The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.

@@

Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found. \citet{Mastropietro2005a} use the N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not completely destroyed by ram pressure or tidal stripping. The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.

%colors
\textit{Star formation histories.} 
Colors and star formation rates are useful since they may point to recent star formation as a part of tidal stripping or dissipative formation. \citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations. \citet{Norris2011} find a similar result with one UCD best fit using older stellar populations. \citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.

@@

In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey that have key data quantifying their morphologies, environments, star formation histories, and kinematics. We use this sample to examine the formation scenarios and evolution of CSSs and dEs/dE,Ns simultaneously as a spectrum of compact galaxies that span the gap from GCs to Es. Because we have derived a complete sample from RESOLVE, our sample contains CCGs at every evolutionary stage. This paper is organized as follows. We describe our parent sample, the RESOLVE survey, in \autoref{resolve} and our comparison sample, the AIMSS catalog, in \autoref{aimss}. Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}. We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}. We next describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}. We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}. In \autoref{discussion}, we present a discussion of our results in the context of CCG formation and evolution. Lastly, the summary and future work are given in \autoref{conclusions}.

@@

\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs. RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages. RESOLVE falls within the footprint of the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}, and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82. With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$. Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.

RESOLVE's exceptional completeness is obtained by making use of multiple redshift surveys to recover galaxies that were missed in SDSS due to fiber collisions, the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, so no one piece meets the magnitude cut and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut. We supplement the SDSS main redshift survey with additional redshifts from archival sources (the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}) to achieve $\sim12\%$ higher completeness in RESOLVE-A and $\sim25\%$ higher completeness in RESOLVE-B.

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star}~\sim~10^{8.9}$~\Msun for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun in the B semester (see Figure 7 in \citet{Eckert2016}). In Figure 1, we plot the stellar masses against the deconvolved, one-component, half-light radius \Reff\ (see \autoref{deconv}) for all of RESOLVE along with the core-only \Reff\ for the CCG sample and see that these limits allow us to reach down to CSSs with sizes and masses similar to cEs.

@@

\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both literature and newly discovered objects. Their process to find new CSSs is as follows. First, a search is conducted in the Hyperleda redshift catalog \citep{Paturel2003} for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$. Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies. Next, Source Extractor is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature. Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted. AIMSS also includes literature data for other UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.5]{galfitexample.eps}
\caption{Shown here are the model outputs from \textsc{Galfit}. The left column shows the UKIDSS $Y$-band image cut out around the galaxy. The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model). The top row shows the one component fit for one of the RESOLVE galaxies, rf0055. As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope. The bottow row shows the two component fit for the same galaxy. We now are able to well fit both the inner bulge and the outer envelope. The residual is much cleaner, although there may be some spiral structure remaining that could require a third component to fit.}
\label{fig:galfit}
\end{center}
\end{figure*}

@@

\noindent We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample. For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits on each galaxy. Deconvolution is especially important since the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for the study of these objects.

\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file. We obtain/construct these items as follows:

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the files paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to have a section for measuring the level of the sky background, and another section for fitting a S\'ersic profile to galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's photometric data (see \autoref{phot} for more details)}

\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}. This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies. The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst. We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}. While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful for constructing a PSF. There are only 24 galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis.

@@

\item With this information, we select stars to use for building our PSF. The limiting parameters are (1) that the flux must be between $5,000-100,000$ counts to ensure no extremely faint or saturated stars are included, (2) that the ellipticity be lt 0.2 to ensure we are selecting round objects, (3) that the effective radius of the star be greater than 1 pixel to avoid selecting hot pixels, and (4) that \texttt{class\_star} is greater than 0.6 to ensure the objects we're picking are most likely stars. We also make sure the stars are not near the image edges, since there can sometimes be image artifacts there. Lastly, we make sure to not include the galaxy we are going to fit, since the cE-like galaxies can sometimes appear to be stars.

>>>>

\title{Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Mark A. Norris\altaffilmark{3}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{Ian Dell'Antonio\altaffilmark{4}}
\author{Callie Hood\altaffilmark{1}}
\author{Samantha Dallas\altaffilmark{4}}
\author{David V. Stark\altaffilmark{1}}
\author{Amanda J. Moffett\altaffilmark{1,5}}
\author{the RESOLVE Team}
\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599, USA; emsnyder@live.unc.edu}
\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
\affil{$^4$Department of Physics, Brown University, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University of Western Australia, 35 Stirling High-
way, Crawley, WA 6009, Australia}
\begin{abstract}
We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments. To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements. The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk. We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs, dEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component. The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated. With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars. We find that CCGs naturally occur in a range of environments from isolated to cluster. We also derive velocity dispersions ($\sigma$) for 8 CCGs from Gemini IFU data and SOAR spectroscopy. Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively. Initial results show 6 CCGs likely following the dissipative formation track and 2 CCGs that are slightly offset to higher $\sigma$.

\end{abstract}

@@

\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range between globular clusters (GCs) and normal elliptical galaxies (Es). Different types of CSSs include compact elliptical galaxies \citep[cEs;][]{Faber1973} and ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001}. There are many unanswered questions about how CSSs form and evolve through time. One fact that makes the study of these compact galaxies so intriguing is their apparent scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size. Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios.

CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.

In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated counterparts (dE,Ns) are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. dEs are typically larger than CSSs with radii ranging up to $\sim800$~pc, whereas dE,Ns may have larger envelopes with a core radius <$800$~pc \citep[e.g.,][]{Norris2014}. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}. There is also some evidence that dE,Ns are progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core radii up to 800~pc. The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevi2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} find cEs separated from other galaxies by $>1$~Mpc.

Environment bears on formation scenarios in different ways. One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CSSs may rather be dissipatively formed like Es. However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process. The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.

@@

Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found. \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping. The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.

%colors
\textit{Star formation histories.} 
Colors and star formation rates are useful since they may point to recent star formation as a part of tidal stripping or dissipative formation. The typical thought is that CSSs are ``red and dead'', and some studies even cut on color when selecting CSS samples \citep{Chilingarian2015}. \citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations. \citet{Norris2011} find a similar result with one UCD best fit using older stellar populations. \citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.

@@

In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey, along with key data quantifying their morphologies, environments, star formation histories, and kinematics. We use this sample to examine the formation scenarios and evolution of CSSs and dEs/dE,Ns simultaneously as a spectrum of compact galaxies that span the gap from GCs to Es. Because we have derived a complete sample from RESOLVE, our sample contains CCGs at every evolutionary stage. This paper is organized as follows. We describe our parent sample, the RESOLVE survey, in \autoref{resolve} and our comparison sample, the AIMSS catalog, in \autoref{aimss}. Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}. We detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}. We describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}. We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}. In \autoref{discussion}, we present a discussion of our results in the context of CCG formation and evolution. Lastly, the summary and future work are given in \autoref{conclusions}.

@@

\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs. RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages. RESOLVE falls within the footprint of the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}, and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82. With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.25\degree$. Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.

RESOLVE's exceptional completeness is obtained by making use of multiple redshift surveys to recover galaxies that were missed in SDSS due to (i) fiber collisions, (ii) the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces so no one piece meets the magnitude cut, and (iii) the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut. We supplement the SDSS main redshift survey with additional redshifts from archival sources, including the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}, to achieve $\sim12\%$ higher completeness in RESOLVE-A and $\sim25\%$ higher completeness in RESOLVE-B \citep{Eckert2015}.

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. To derive the stellar mass completeness limits of RESOLVE, \citet{Eckert2016} use the known stellar masses and magnitudes of all RESOLVE galaxies to determine the stellar mass limit above which no more than 2\% of objects have an $r$-band magnitude fainter than the stated magnitude completeness limit. These values are M$_{\star}~\sim~10^{8.9}$~\Msun~for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun~in the B semester \citep[Figure 8 in ][]{Eckert2016}. These stellar mass completeness limits allow us to reach down to CSSs with sizes and masses similar to cEs (see \autoref{morph} for more details).

@@

\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects. The AIMSS CSS discovery process was as follows. First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging). The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies. Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature. After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions. AIMSS also includes literature data for previously known UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.5]{galfitexample.eps}
\caption{Model inputs and outputs from \textsc{Galfit}. The left column shows the UKIDSS $Y$-band image cutout around the galaxy. The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model). The top row shows the one component fit for one of the RESOLVE galaxies, rf0055. As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope. The bottom row shows the two component fit for the same galaxy. We are now  able to fit both the inner bulge and the outer envelope. The residual is much cleaner, although there may be some spiral structure remaining.}
\label{fig:galfit}
\end{center}
\end{figure*}

@@

\noindent We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample. For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits to each galaxy. Deconvolution is especially important since the smallest galaxies in RESOLVE are most affected by seeing, and accurate radius measurements are crucial for the study of these objects.

\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file. We obtain or construct these items as follows:

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile to the galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}

\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}. This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies. The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst. We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}. While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful when constructing the PSF image. There are only 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.

@@

\item With this information, we select stars to use for building our PSF. The limiting parameters are (1) that the flux must be between $5,000-100,000$ counts to ensure no extremely faint or saturated stars are included, (2) that the ellipticity be less than 0.2 to ensure we are selecting round objects, (3) that the effective radius of the star be greater than 1 pixel to avoid selecting hot pixels, and (4) that \texttt{class\_star} is greater than 0.6 to ensure the objects we're picking are most likely stars. We also make sure the stars are not near the image edges, since there can sometimes be image artifacts there. Lastly, we make sure to not include the galaxy we are going to fit, since the cE-like galaxies can sometimes appear to be stars.
